Notes for ISIPTA poster

### 2016-07-15 asce-paper.tex
organizing sec 4

\subsection{Right-censored Lifetimes}

@@

\subsection{Bayesian Estimation of Component Scale Parameter}

@@

\subsection{RUL using the Survival Signature}

@@

\subsection{Posterior Predictive Distribution}

@@

\subsection{Optimizing over Sets of Parameters}

@@

\section{elicitation}

@@

>>>>

We now consider a system of arbitrary layout,
consisting of components of $K$ types.
This system is observed until time $\tnow$,
leading to censored observations,
and we will explain in Section~\ref{sec:lambdawithcens}
how the scale parameter $\lambda_k$ for component type $k$
can be estimated in this situation.
%
Section~\ref{sec:sysrelwithsurvsign} describes then
how the system relibility function can be efficiently obtained using the survival signature.
%
For this, we need the posterior predictive distribution
of the number of components function at times $t > \tnow$,
which we will derive in Section~\ref{sec:postpred}.
%
Finally, in Section~\ref{sec:optimize} we describe how
the lower and upper bound for the system reliability function
are obtained when prior parameters $(\nkz,\ykz)$
vary in sets $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
defining sets $\MkZ$ of prior distributions over $\lambda_k$,
as introduced in Section~\ref{sec:modforsurpr}.

\subsection{Bayesian Estimation of Component Scale Parameter with Right-censored Lifetimes}
\label{sec:lambdawithcens}

@@

@@

\subsection{System Reliability using the Survival Signature}
\label{sec:sysrelwithsurvsign}

@@

\subsection{Posterior Predictive Distribution}
\label{sec:postpred}

@@

\subsection{Optimizing over Sets of Parameters}
\label{sec:optimize}

@@

\section{Elicitation of prior parameter sets}

@@

\section{Examples}

\section{Concluding Remarks}
